### 2020-03-22 paper/sections/introduction.tex
proofread

\section{Introduction}
\label{sec: introduction}

\IEEEPARstart{W}{ith} the great success of deep learning in computer vision, this decade has witnessed an explosion of deep learning-based computer vision-based applications. Because of the huge computational resource consumption for deep learning applications (e.g., inferring an image on VGG19~\cite{VGG19} requires $20$ GFLOPs of GPU resource), in today's online computer vision-based applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load.

To reduce the upload traffic load, it is straightforward that an image should be compressed before one uploads it. Though JPEG has been used as the \emph{de facto} image compression and encapsulation method, its performance for the deep computer vision models is not satisfactory. Liu et al.~\cite{DeepN-JPEG} showed that by re-designing the quantization table in the default JPEG configuration, one can compress an image to a smaller version while maintaining the same inference accuracy for a deep computer vision model. However, such quantization solutions usually assume the inference model is fixed.

We then raise an intuitive question: to make it practically useful, can we select the JPEG configuration adaptively for different online computer vision-based services, without any prior knowledge of the original model and input images? In this paper, we propose a reinforcement learning-based framework to select JPEG configurations adaptively. In our solution, we tackle the following design challenges.

@@

\item \emph{Lack of information about the cloud-based computer vision models.} Previous studies~\cite{DeepN-JPEG, torfason2018towards, gueguen2018faster}, generally assume that the details of the computer vision models are available so that they can adjust the JPEG configuration according to the model structure, e.g., one can train a model to determine the JPEG configuration by plugging the original computer vision model into it. However, the structure details of online computer vision models are usually proprietary and not open to the users.

\item \emph{Different cloud-based computer vision models need different JPEG configurations.} As an adaptive JPEG configuration solution, we target to provide a solution that is adaptive to different online computer vision-based services, i.e., it can \emph{generate} JPEG configuration for different models. However, today's cloud-based computer vision algorithms, based on deep and convolutional computations, are quite hard to understand. The same compression quality level could lead to a totally different accuracy performance. Some examples are shown in Figure~\ref{fig: compress_accuracy}: picture 1a and 1b, 2a and 2b are visually similar for human beings, but the deep learning model gives different inference results, only because they are compressed at different quality levels. And such a relationship is not apparent, e.g., picture 3b is highly compressed and looks destroyed comparing to picture 3a, but the deep learning model can still recognize it. This phenomenon is also presented in~\cite{delac2005effects} and commonly seen in adversarial neural network researches~\cite{yuan2019adversarial, evtimov2018robust}.

\item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which image should be compressed to which quality level, as in conventional supervised deep learning tasks. In practice, such an image compression module is usually utilized in an online manner, and the solution has to learn from the images it uploads automatically. 
\end{itemize}

\begin{figure*}[htbp]
%	\begin{tabular}{cc}
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 150 0 150, clip]{figures/donut_q75.jpeg}}
		\centerline{(1a) Q=75}
%		\centerline{Face++ prediction=["donut"]}
		\centerline{Face++ prediction \ = \ ["donut"]}
		\vspace{0.4cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 150 0 150, clip]{figures/donut_q55.jpeg}}
		\centerline{(1b) Q=55}
%		\centerline{Face++ prediction=[]}
		\centerline{Face++ prediction \ = \ ["biscuit"]}
		\vspace{0.4cm}
	\end{minipage}
	\vfill	
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0]{figures/chameleon_q75.jpeg}}
		\centerline{(2a) Q=75}
% 		\centerline{\quad Baidu prediction=["chameleon"]}
		\centerline{Baidu prediction \ = \ ["chameleon"]}
		\vspace{0.4cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0]{figures/chameleon_q55.jpeg}}
		\centerline{(2b) Q=55}
% 		\centerline{\qquad Baidu prediction=["electric fan"]}
 		\centerline{Baidu prediction \ = \ ["electric fan"]}
 		\vspace{0.4cm}
	\end{minipage}
	\vfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0, clip]{figures/tiger_highq.jpeg}}
		\centerline{(3a) Q=75}
%		\centerline{Baidu prediction=["leopard"]}
		\centerline{Baidu prediction \ = \ ["leopard"]}
		\vspace{0.3cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0, clip]{figures/tiger_lowq.jpeg}}
		\centerline{(3b) Q=5}
%		\centerline{Baidu prediction=["leopard"]}
		\centerline{Baidu prediction \ = \ ["leopard"]}
		\vspace{0.3cm}
	\end{minipage}
%	\end{tabular}
	\caption{The prediction of a deep learning model is not completely related to the input image's quality, making it difficult to use a fixed compression quality for all images. For image 1a, 1b and 2a, 2b, minor changes cause different predictions though they are visually similar; for image 3a and 3b, the cloud model still output correct label from a severely compressed image though they look very different}
	\label{fig: compress_accuracy}
%	\vspace{-0.1cm}
\end{figure*}

To address the above challenges, we present a reinforcement learning-based solution, called AdaCompress\footnote{We open-sourced AdaCompress that works with online computer vision-based APIs at \url{https://github.com/hosea1008/AdaCompress}}, to choose the proper compression quality level for an image to a computer vision model on the cloud, in an online manner. This paper is an extension of our earlier conference paper~\cite{2019adacompress}, with the following contributions:

@@

$\rhd$ We build a reinforcement learning-based framework to train the agent in the above environment. The agent can learn to choose a proper compression quality level for an input image after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and data size. Based on~\cite{2019adacompress}, we further propose an \emph{explore-exploit} mechanism to let the agent switch between ``sceneries''. In particular, after deploying the agent, an \emph{inference-estimate-retrain} solution is designed to restart the training once the scenery changes and the existing running agent cannot guarantee the original accuracy performance.

$\rhd$~~In this journal extension, we provide more analysis and insights on our design. By analyzing the Deep Q-learning Network-based agent's behaviors using Grad-Cam~\cite{grad-cam}, we provide the reasons that the agent chooses a specific compression quality level. We reveal that images containing large smooth areas are more sensitive to compression, while images with complex textures are more robust to compression for computer vision models.

$\rhd$ We evaluate our system on representative cloud deep learning services, including Amazon Rekognition~\cite{amazon_rekognition}, Face++~\cite{face++_service} and Baidu Vision~\cite{baidu_vision}, and show that our design can reduce the upload traffic load by up to $1/2$ while maintaining comparable overall accuracy. Compared to baseline DeepN-JPEG~\cite{DeepN-JPEG}, the overall accuracy of AdaCompress is $8\%$ higher when they have similar compressed image size.

% \begin{itemize}
% 	\item First, we completed designing agent caching strategy work mentioned in our previous version's future work~\cite{2019adacompress}, adding the model query state in previous inference-estimate-retrain mechanism to avoid unnecessary upload traffic load in the retraining phase. Once capturing the scenery change, comparing to the previous mechanism that retrains from scratch directly, in our new mechanism, AdaCompress switches into model query state and loads a suitable RL agent model, achieving a lower upload traffic load. In the experiment, we use the FLIR Thermal Dataset instead of the previous DNIM Dataset to act as a nighttime scenery since thermal sensors capture gray-scaled thermal images in the nighttime, and the experiment result shows that our design can cut down the uploading file size overhead effectively.
% 	\item Second, for the comparison purpose, we implement the DeepN-JPEG framework according to~\cite{DeepN-JPEG} and evaluate the size reduction and accuracy performance. Our experiment shows that AdaCompress and DeepN-JPEG both decrease the uploading file size overhead more than 1/2, but the inference accuracy of AdaCompress is 8\% higher than that of DeepN-JPEG. Moreover, we provide illustrative image examples to present that AdaCompress compresses images more adaptively to achieve higher accuracy.
% 	\item Last but not least, we re-organize and amend the manuscript significantly to be easier to follow.
% \end{itemize}
The rest of this paper is organized as follows. We discuss related works in Sec.~\ref{sec: related_works}. In Sec.~\ref{sec: design} we present our framework and detailed design. We present our solution's performance in Sec.~\ref{sec: evaluation} and conclude the paper in Sec.~\ref{sec: conclusion}.

>>>>

\section{Introduction}
\label{Section: introduction}

\IEEEPARstart{W}{ith} the great success of deep learning in computer vision, this decade has witnessed an explosion of deep learning-based computer vision-based applications. Because of the enormous computational resource consumption for deep learning applications (e.g., inferring an image on VGG19~\cite{VGG19} requires $20$ GFLOPs of GPU resource), in today's online computer vision-based applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load.

To reduce the upload traffic load, one should compress the image before uploading it. Though JPEG has been used as the \emph{de facto} image compression and encapsulation method, its performance for the deep computer vision models is not satisfactory. Liu et al.~\cite{DeepN-JPEG} showed that by re-designing the quantization table in the default JPEG configuration, one can compress an image to a smaller version while maintaining the comparable inference accuracy for a deep computer vision model. However, such quantization solutions usually assume the inference model is fixed. 
%To reduce the upload traffic load, it is straightforward that an image should be compressed before one uploads it.

We then raise an intuitive question: to make it practically useful, can we select the JPEG configuration adaptively for different online computer vision-based services, without any prior knowledge of the original model? In this paper, we propose a reinforcement learning-based framework to select JPEG configurations adaptively. In our solution, we tackle the following design challenges.
% and input images

@@

\item \emph{Lack of information about the cloud-based computer vision models.} Previous studies~\cite{DeepN-JPEG, torfason2018towards, gueguen2018faster}, generally assume that the details of the computer vision models are available so that they can adjust the JPEG configuration according to the model structure, e.g., one can train a model to determine the JPEG configuration by plugging the original computer vision model into it. However, the structural details of online computer vision models are usually proprietary and not open to the users.

\item \emph{Different cloud-based computer vision models need different JPEG configurations.} As an adaptive JPEG configuration solution, we target to provide a solution that is adaptive to different online computer vision-based services, i.e., it can \emph{generate} JPEG configuration for different models. However, today's cloud-based computer vision algorithms, based on deep and convolutional computations, are quite hard to understand. The same compression quality level could lead to a different accuracy performance. Some examples are shown in Figure~\ref{fig: compress_accuracy}: picture 1a and 1b, 2a and 2b are visually similar for human beings, but the deep learning model gives different inference results, only because they are compressed at different quality levels. And such a relationship is not apparent, e.g., picture 3b is highly compressed and looks destroyed comparing to picture 3a, but the deep learning model can still recognize it. This phenomenon is also presented in~\cite{delac2005effects} and commonly seen in adversarial neural network researches~\cite{yuan2019adversarial, evtimov2018robust}.

\item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which image should be compressed at which quality level, as in conventional supervised deep learning tasks. In practice, such an image compression module is usually utilized in an online manner, and the solution has to learn from the images it uploads automatically. 
\end{itemize}

\begin{figure*}[htbp]
%	\begin{tabular}{cc}
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 150 0 150, clip]{figures/donut_q75.jpeg}}
		\centerline{(1a) Q=75}
%		\centerline{Face++ prediction=["donut"]}
		\centerline{Face++ prediction \ = \ [``donut'']}
		\vspace{0.4cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 150 0 150, clip]{figures/donut_q55.jpeg}}
		\centerline{(1b) Q=55}
%		\centerline{Face++ prediction=[]}
		\centerline{Face++ prediction \ = \ [``biscuit'']}
		\vspace{0.4cm}
	\end{minipage}
	\vfill	
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0]{figures/chameleon_q75.jpeg}}
		\centerline{(2a) Q=75}
% 		\centerline{\quad Baidu prediction=["chameleon"]}
		\centerline{Baidu prediction \ = \ [``chameleon'']}
		\vspace{0.4cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0]{figures/chameleon_q55.jpeg}}
		\centerline{(2b) Q=55}
% 		\centerline{\qquad Baidu prediction=["electric fan"]}
 		\centerline{Baidu prediction \ = \ [``electric fan'']}
 		\vspace{0.4cm}
	\end{minipage}
	\vfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0, clip]{figures/tiger_highq.jpeg}}
		\centerline{(3a) Q=75}
%		\centerline{Baidu prediction=["leopard"]}
		\centerline{Baidu prediction \ = \ [``leopard'']}
		\vspace{0.3cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0, clip]{figures/tiger_lowq.jpeg}}
		\centerline{(3b) Q=5}
%		\centerline{Baidu prediction=["leopard"]}
		\centerline{Baidu prediction \ = \ [``leopard'']}
		\vspace{0.3cm}
	\end{minipage}
%	\end{tabular}
	\caption{The prediction of a deep learning model is not completely related to the input image's quality, making it difficult to use a fixed compression quality for all images. For image 1a, 1b and 2a, 2b, minor changes cause different predictions though they are visually similar; for image 3a and 3b, the cloud-based model still output correct label from a severely compressed image though they look very different}
	\label{fig: compress_accuracy}
%	\vspace{-0.1cm}
\end{figure*}

To address the above challenges, we present a reinforcement learning-based solution, called AdaCompress\footnote{We open-sourced AdaCompress that works with online computer vision-based APIs at \url{https://github.com/hosea1008/AdaCompress}}, to choose a proper compression quality level for an image to a computer vision model on the cloud-end, in an online manner. This paper is an extension of our earlier conference paper~\cite{2019adacompress}, with the following contributions:

@@

$\rhd$ We build a reinforcement learning-based framework to train the agent in the above environment. The agent can learn to choose a proper compression quality level for an input image after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and data size. We further propose an \emph{explore-exploit} mechanism to let the agent switch between ``sceneries''. In particular, after deploying the agent, an \emph{inference-estimation-querying-retraining} solution is designed to switch the RL agent intelligently once the scenery changes and the existing running agent cannot guarantee the original accuracy performance.
%re-load or re-train a RL agent intelligently
%restart the training
%Based on~\cite{2019adacompress},

$\rhd$~~In this journal extension, we provide more analysis and insights on our design. We notice that the Deep Q-learning Network-based agent's behaviors are various for different input image “sceneries” and backend cloud services. By analyzing the agent's behaviors using Grad-Cam~\cite{grad-cam}, we provide the reasons that the agent chooses a specific compression quality level. We reveal that images containing large smooth areas are more sensitive to compression, while images with complex textures are more robust to compression for computer vision models.

$\rhd$ We evaluate our system on representative cloud-based deep learning services, including Amazon Rekognition~\cite{amazon_rekognition}, Face++~\cite{face++_service} and Baidu Vision~\cite{baidu_vision}. We show that our design can reduce the upload traffic load by up to $1/2$ while maintaining comparable overall accuracy. Compared to baseline DeepN-JPEG~\cite{DeepN-JPEG}, the overall accuracy of AdaCompress is $8\%$ higher when they have similar compressed image size.

% \begin{itemize}
% 	\item First, we completed designing agent caching strategy work mentioned in our previous version's future work~\cite{2019adacompress}, adding the model query state in previous inference-estimate-retrain mechanism to avoid unnecessary upload traffic load in the retraining phase. Once capturing the scenery change, comparing to the previous mechanism that retrains from scratch directly, in our new mechanism, AdaCompress switches into model query state and loads a suitable RL agent model, achieving a lower upload traffic load. In the experiment, we use the FLIR Thermal Dataset instead of the previous DNIM Dataset to act as a nighttime scenery since thermal sensors capture gray-scaled thermal images in the nighttime, and the experiment result shows that our design can cut down the uploading file size overhead effectively.
% 	\item Second, for the comparison purpose, we implement the DeepN-JPEG framework according to~\cite{DeepN-JPEG} and evaluate the size reduction and accuracy performance. Our experiment shows that AdaCompress and DeepN-JPEG both decrease the uploading file size overhead more than 1/2, but the inference accuracy of AdaCompress is 8\% higher than that of DeepN-JPEG. Moreover, we provide illustrative image examples to present that AdaCompress compresses images more adaptively to achieve higher accuracy.
% 	\item Last but not least, we re-organize and amend the manuscript significantly to be easier to follow.
% \end{itemize}
The rest of this paper is organized as follows. We discuss related works in Section.~\ref{Section: related_works}. We present our framework and detailed design in Section.~\ref{Section: design}. We present our solution's performance in Section.~\ref{Section: evaluation} and conclude the paper in Section.~\ref{Section: conclusion}.

### 2020-03-22 paper/sections/relatedwork.tex
proofread

\section{Related Works}
\label{sec: related_works}

@@

Though the accurate term is still for the community to debate, we use ``model compression'' to represent the studies on \emph{compressing} and \emph{moving} the deep learning models close to users. Many studies tried to compress the deep learning models and deploy them \emph{locally}~\cite{prun_quanti, pruning_han, quantize, quantize_3bit, quantization, structured_pruning}, i.e., running an alternative ``smaller version'' of a computer vision model at the user-side, to avoid the image upload so that to improve the inference efficiency. Other studies proposed to run a part of a deep learning model \emph{locally}~\cite{ILP_Decoupling, jalad, Edge_LBP, Neurosurgeon}, by decoupling the deep learning model into different parts, e.g., based on the layers in the deep learning model, so that a part of the inference is done \emph{locally} to save some execution time. However, these solutions usually need to \emph{re-train} the model, using the original dataset of the model, which is not practical for today's online computer vision-based services that are merely a black box to end-users, e.g., in the form of a RESTful API.

@@

Data compression solutions study how to compress the original data (e.g., a video or image) to be inferred by the cloud-based deep learning model, so that less traffic is used to upload the data to improve inference speed. Conventional data compression solutions (e.g., JPEG~\cite{jpeg}, WebP~\cite{calore2010meet} and JPEG2000~\cite{rabbani2002jpeg2000}, etc.) and some recent neural network-based compression solutions~\cite{toderici2017full, theis2017lossy, toderici2015variable, rippel2017real} are initially designed for the Human-Visual System. In recent years, researchers found that the human visually optimized-based data compression solutions are not usually applicable to deep learning vision models. Delac et al.~\cite{delac2005effects} observed that, in some cases, a higher compression quality level does not always deteriorates the model inference performance, even improves it slightly. Dodge et al.~\cite{dodge2016understanding} further discovered that besides the JPEG compression, four types of quality distortions (blur, noise, contrast, and the JPEG2000 compression~\cite{rabbani2002jpeg2000}) can also affect the inference performance of the deep learning models. Liu et al.~\cite{DeepN-JPEG} proposed that the conventional JPEG image compression framework is designed for the Human-Visual System which is not suitable for the deep neural network, leading to computer vision models' inference performance degradation at lower images' compression quality levels. %% \\

Based on these insights, Robert et al.~\cite{torfason2018towards} tried to train the deep neural network from the compressed representations of an auto-encoder. Chao et al.~\cite{chao2011preserving} proposed using variable quantization which is supported by the JPEG standard extension syntax~\cite{dis199110918} to compress the macroblocks in images. Furthermore, they~\cite{chao2013design} designed a quantization table based on the observed impact of scale-space processing on the discrete cosine transform (DCT) basis functions for JPEG images, achieving similar inference performance with reduced image size. Liu et al.~\cite{DeepN-JPEG} proposed DeepN-JPEG that re-designs the quantization table by linking statistical information of defined features and defined quantization values so that the compressed image size is reduced for deep learning models. Chamain et al.~\cite{2019quannet} proposed a joint optimization of image classification network coupled with the image quantization, achieving image size reduction of JPGE2000~\cite{rabbani2002jpeg2000} encoded images. Recently, Lionel et al.~\cite{gueguen2018faster} presented a new type of neural network that infers directly from the discrete cosine transform (DCT) coefficients in the middle of the JPEG codec. Baluja et al.~\cite{baluja2019task} proposed task-specific compression that compresses images based on the end-use of images. %% \\

However, such proposals all need one to understand the characteristics of the cloud-based deep learning model and have access to the original training dataset, to \emph{generate} the appropriate color space and/or compression schemes. To the best of our knowledge, we are the first to propose an adaptive compression configuration solution named AdaCompress~\cite{2019adacompress} that learns the optimal compression quality level to achieve an expected inference accuracy and upload image size, only from the online inference results, without knowing details of the model structures.

In this extension paper, we improve previous \emph{inference-estimate-retrain} mechanism to cut down the upload image size overhead effectively, add DeepN-JPEG comparative experiment, and amend the manuscript significantly. Especially on the DeepN-JPEG comparative experiment, since Liu et al.~\cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on ImageNet by using four state-of-the-art DNN models (AlexNet~\cite{AlexNet-krizhevsky2012imagenet}, VGG~\cite{VGG-simonyan2014very}, GoogLeNet~\cite{GoogleNet-szegedy2015going} and ResNet~\cite{ResNet-he2016deep}) on local terminal devices, which are different from online computer vision-based services. For comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using ImageNet and the metrics in Sec.~\ref{subsec:metrics} on three cloud-based deep learning services (Amazon Rekognition, Face++ and Baidu Vision), the same experiment configuration as AdaCompress's.

>>>>

\section{Related Works}
\label{Section: related_works}

@@

Though the accurate term is still for the community to debate, we use ``model compression'' to represent the studies on \emph{compressing} and \emph{moving} the deep learning models close to users. Many studies tried to compress the deep learning models and deploy them \emph{locally}~\cite{prun_quanti, pruning_han, quantize, quantize_3bit, quantization, structured_pruning}, i.e., running an alternative ``smaller version'' of a computer vision model at the user-side, to avoid the image upload so that to improve the inference efficiency. Other studies proposed to run a part of a deep learning model \emph{locally}~\cite{ILP_Decoupling, jalad, Edge_LBP, Neurosurgeon}, by decoupling the deep learning model into different parts, e.g., based on the layers in the deep learning model, so that a part of the inference is done \emph{locally} to save some execution time. However, these solutions usually need to re-train the model using the original dataset of the model, which is not practical for today's online computer vision-based services that are merely a black box to end-users, e.g., in the form of a RESTful API.

@@

Data compression solutions study how to compress the original data (e.g., a video or image) to be inferred by the cloud-based deep learning model so that less traffic is used to upload the data to improve inference speed. In recent years, researchers found that conventional human visually optimized-based data compression solutions (e.g., JPEG~\cite{jpeg}, WebP~\cite{calore2010meet} and JPEG2000~\cite{rabbani2002jpeg2000}, etc.) and some recent neural network-based compression solutions~\cite{toderici2017full, theis2017lossy, toderici2015variable, rippel2017real} are not usually applicable to deep learning vision models. Liu et al.~\cite{DeepN-JPEG} revealed that the conventional JPEG image compression framework is designed for the Human-Visual System, which is not suitable for the deep neural network, leading to the computer vision model's inference performance degradation. Dodge et al.~\cite{dodge2016understanding} further discovered that besides the JPEG compression, four types of quality distortions (blur, noise, contrast, and the JPEG2000 compression~\cite{rabbani2002jpeg2000}) can also affect the inference performance of the deep learning models. Delac et al.~\cite{delac2005effects} observed that, in some cases, a high compression quality level does not always reduce the model inference accuracy. %% \\

Based on these insights, Robert et al.~\cite{torfason2018towards} tried to train the deep neural network from the compressed representations of an auto-encoder. Chao et al.~\cite{chao2011preserving} proposed using variable quantization, which is supported by the JPEG standard extension syntax~\cite{dis199110918} to compress the macroblocks in images. Furthermore, they~\cite{chao2013design} designed a quantization table based on the observed impact of scale-space processing on the discrete cosine transform (DCT) basis functions for JPEG images, achieving similar inference performance while reducing the image size overhead effectively. Liu et al.~\cite{DeepN-JPEG} proposed DeepN-JPEG that re-designs the quantization table by linking statistical information of defined features and defined quantization values so that the compressed image size is reduced for deep learning models. Chamain et al.~\cite{2019quannet} proposed a joint optimization of image classification network coupled with the image quantization, achieving image size reduction of JPGE2000~\cite{rabbani2002jpeg2000} encoded images. Recently, Lionel et al.~\cite{gueguen2018faster} presented a new type of neural network that infers directly from the discrete cosine transform coefficients in the middle of the JPEG codec. Baluja et al.~\cite{baluja2019task} proposed task-specific compression that compresses images based on the end-use of images. %% \\

However, such proposals all need one to understand the characteristics of the cloud-based deep learning model and have access to the original training dataset,  \emph{generating} the appropriate compression schemes. To the best of our knowledge, we are the first to propose an adaptive compression configuration solution that learns the optimal compression quality level to achieve an expected inference accuracy and upload image size, only from the online inference results, without knowing details of the model structures.

In this journal extension, we improve the previous \emph{inference-estimate-retrain} mechanism to cut down the upload image size overhead effectively, add DeepN-JPEG comparative experiment, and amend the manuscript significantly. Especially in the DeepN-JPEG comparative experiment, since Liu et al.~\cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on ImageNet by using four state-of-the-art DNN models (AlexNet~\cite{AlexNet-krizhevsky2012imagenet}, VGG~\cite{VGG-simonyan2014very}, GoogLeNet~\cite{GoogleNet-szegedy2015going} and ResNet~\cite{ResNet-he2016deep}) on local edge devices, which are different from online computer vision-based services, for comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using ImageNet and the metrics in Subsection.~\ref{subsec:metrics} on three cloud-based deep learning services (Amazon Rekognition, Face++ and Baidu Vision).
